RadLib: a radiative heat transfer model library for CFD

### 2020-11-25 manuscript/manuscript.tex
Draft text of impact section, fixes to references

As far as I'm aware, there isn't an easy way to incorporate radiative heat transfer into a CFD simulation. Most cases use optically thin assumption (which works in some cases, but not in others) or neglect radiation entirely (also applicable sometimes, but not always). [Refer to TNF website radiation page here.] Unfortunately, this means that when you simulation some configuration in which radiation might be important to the overall heat transfer, you won't get accurate simulation results. Furthermore, if your study is about something else entirely, your radiation model (or lack thereof) becomes a source of error that may be very difficult to separate from other sources of error in your simulation study (i.e. soot modeling studies). As of right now, if you want any detailed radiation treatment, you have to code it yourself, which is difficult and requires external validation.

RadLib can make researchers' lives easier by providing a library of prevalidated radiation models that can be switched out with no difficulty. Additional models can be added easily using the provided modular framework. Researchers can even use Radlib as a tool for comparing models. No need to code multiple different complex radiation models yourself just to decide which one works best for your simulation. And no need to puzzle through the literature to figure our which model(s) might be best for your simulation, either; instead, you can test them yourself. It saves tons of time and effort that researchers can now put toward results rather than code or model development.

By putting all these models side by side in a modular framework, RadLib also provides a structure on which new or altered radiation models can be tested against existing ones. Maybe more comparative studies can be done, especially for more complex simulation cases. We plan to add radiation models as appropriate to RadLib, too.

RadLib opens up new horizons for CFD simulations, especially in combustion cases. It is designed such that it can be easily incorporated into existing research codes. Our group plans to use it with ODT [CITE OTHER SOFTWAREX PAPER HERE?] alongside soot model library (in development) to study late-flame phenomena such as soot oxidation, flame extinction, and soot-flame breakthrough. These topics in particular are difficult because they require accurate simulation data over a relatively long computational time in addition to good models for both soot chemistry (which is an active research area) and radiation heat transfer (which is the difficult part that RadLib can solve). Using RadLib for such studies allows us to separate and quantify sources of error that may occur due to various models, which is super difficult if you only have one model to work with or it hasn't been validated well.

RadLib can also be used outside of combustion CFD research for anything involving radiative heat transfer. Potential research areas that could benefit include atmospheric and climate sciences, interstellar phenomena, improving efficiency of energy-producing processes, safety in chemical plant design, etc. We aren't experts in these areas, but radiative heat transfer is a universal phenomena that applies to any system or process that involves heat transfer.

This software has not been used outside of the current research group, and it is not used in any commercial settings at this time.

>>>>

Radiative heat transfer models are historically difficult to implement in CFD codes due to their complexity and high computational costs. Neglecting radiation or using simple models like the optically thin assumption is adequate for some cases with simple geometry or limited chemical reactions, but most simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results. In such cases, radiation models that are incorrectly implemented or inappropriate for the simulation parameters can become additional sources of error that may be extremely difficult to separate from existing sources or error. Currently, researchers that require detailed radiation modeling must code and validate it themselves at the expense of valuable research time and funding.

RadLib makes researchers' work easier by consolidating various approaches into a modular library of interchangeable, prevalidated radiation models. Additionally, RadLib's modular framework is designed to easily accommodate new models as well, allowing researchers to compare new or existing models with very little overhead. Sometimes, it is not clear which radiation model may be the best fit for a particular simulation. When simulations are especially complex or computationally expensive, researchers may have to extrapolate from theory and literature to choose an appropriate radiation model rather than testing for their specific case. RadLib is designed to ease both of these obstacles by facilitating comparison between radiation models through a common interface and providing a practical means of testing various models without the restriction of prespecified geometry or case parameters. With RadLib, researchers can put more of their time and effort into useful results rather than code or model development.

Currently, RadLib is only used within the authors' research group, where it is applied to combustion CFD simulations using the One-Dimensional Turbulence (ODT) model \cite{Stephens_2020}, but its design and structure as a C++ library allows it to be incorporated easily into existing codes. It can be applied to  research questions in various other fields involving radiative heat transfer as well, including energy engineering or atmospheric and climate sciences. Radiation is a universal phenomenon, and RadLib can assist researchers in many areas with systems and processes that involve heat transfer.
